Testing Gravity Using Type Ia Supernovae Discovered by Next Generation Wide Field Imaging Surveys

### 2019-03-18 doc/article.tex
changes to author list requested
new author list

@@

O.~Graur\footnotemark[7]\textsuperscript{,}\footnotemark[8]\textsuperscript{,}\footnotemark[9],
\footnotetext[7]{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
\footnotetext[8]{Department of Astrophysics, American Museum of Natural History, New York, NY 10024, USA}
\footnotetext[9]{NSF Astronomy and Astrophysics Postdoctoral Fellow}
R.~Graziani\footnotemark[10],
\footnotetext[10]{Universit\'e Clermont Auvergne, CNRS/IN2P3, Laboratoire de

@@

R.~Hlo\u{z}ek\footnotemark[3]\textsuperscript{,}\footnotemark[11],

@@

\footnotetext[11]{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, ON, M5S 3H4}
C.~Howlett\footnotemark[12],
\footnotetext[12]{International Centre for Radio Astronomy Research, The University of Western Australia, Crawley, WA 6009, Australia}
D.~Huterer\footnotemark[13],
\footnotetext[13]{Department of Physics, University of Michigan, 450 Church Street, Ann

@@

P.-F.~Leget\footnotemark[14],
\footnotetext[14]{Laboratoire de Physique Nucl\'eaire et de Hautes Energies, Sorbonne Universit\'e, CNRS-IN2P3, 4 Place Jussieu, 75005 Paris, France}    

@@

J.~Nordin\footnotemark[15],
\footnotetext[15]{Institut fur Physik, Humboldt-Universitat zu Berlin, Newtonstr. 15, 12489 Berlin, Germany}
P.~Nugent\footnotemark[16],
\footnotetext[16]{Computational Research Division, Lawrence Berkeley National Laboratory, 

@@

S.~Perlmutter\footnotemark[1]\textsuperscript{,}\footnotemark[17],
\footnotetext[17]{Department of Physics, University of California Berkeley, Berkeley, CA 94720}
N.~Regnault\footnotemark[14],

@@

M.~Rigault\footnotemark[10],

@@

A.~Shafieloo\footnotemark[18],
\footnotetext[18]{Korea Astronomy and Space Science Institute, Yuseong-gu, Daedeok-daero 776, Daejeon 34055, Korea}
A.~Slosar\footnotemark[19],
\footnotetext[19]{Brookhaven National Laboratory, Physics Department, Upton, NY

@@

R.~B.~Tully\footnotemark[20],
\footnotetext[20]{Institute for Astronomy, University of Hawaii, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
M.~White\footnotemark[1]\textsuperscript{,}\footnotemark[17],
M.~Wood-Vasey\footnotemark[21]
\footnotetext[21]{PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA} 

@@

\footnotemark[22],
\footnotetext[22]{Department of Physics, Lower Mountjoy, South Rd, Durham DH1 3LE, United Kingdom} 
Robert Armstrong\footnotemark[23],
\footnotetext[23]{Lawrence Livermore National Laboratory, Livermore, CA, 94550} 
Jacobo Asorey\footnotemark[18],
Carlo Baccigalupi\footnotemark[24]\textsuperscript{,}\footnotemark[25]\textsuperscript{,}\footnotemark[26],
\footnotetext[24]{SISSA - International School for Advanced Studies, Via Bonomea 265, 34136 Trieste, Italy} 
\footnotetext[25]{IFPU - Institute for Fundamental Physics of the Universe, Via Beirut 2, 34014 Trieste, Italy} 
\footnotetext[26]{INFN - National Institute for Nuclear Physics, Via Valerio 2, I-34127 Trieste, Italy} 
Maciej Bilicki\footnotemark[27],
\footnotetext[27]{Center for Theoretical Physics, Polish Academy of Sciences, al. Lotnik\'{o}w 32/46, 02-668, Warsaw, Poland} 
Julian Borrill\footnotemark[16], 
Elizabeth Buckley-Geer\footnotemark[28],
\footnotetext[28]{Fermi National Accelerator Laboratory, Batavia, IL 60510} 

@@

Cora Dvorkin\footnotemark[29],
\footnotetext[29]{Department of Physics, Harvard University, Cambridge, MA 02138, USA} 
Simon Foreman\footnotemark[30],
\footnotetext[30]{Canadian Institute for Theoretical Astrophysics, University of Toronto, Toronto, ON M5S 3H8, Canada} 
Llu\'is Galbany\footnotemark[21],
Juan Garc\'ia-Bellido\footnotemark[31]\textsuperscript{,}\footnotemark[32],
\footnotetext[31]{Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain} 
\footnotetext[32]{Universidad Aut\'{o}noma de Madrid, 28049, Madrid, Spain} 
Martina Gerbino\footnotemark[33],
\footnotetext[33]{HEP Division, Argonne National Laboratory, Lemont, IL 60439, USA} 
Mandeep S.S. Gill\footnotemark[34]\textsuperscript{,}\footnotemark[35]\textsuperscript{,}\footnotemark[36],
\footnotetext[34]{Kavli Institute for Particle Astrophysics and Cosmology, Stanford 94305} 
\footnotetext[35]{Stanford University, Stanford, CA 94305} 
\footnotetext[36]{SLAC National Accelerator Laboratory, Menlo Park, CA 94025} 
Larry Gladney\footnotemark[37],
\footnotetext[37]{Department of Physics, Yale University, New Haven, CT 06520} 
Saurabh W.~Jha\footnotemark[38],
\footnotetext[38]{Department of Physics and Astronomy, Rutgers, the State University of New Jersey, 136 Frelinghuysen Road, Piscataway, NJ 08854, USA} 
Johann Cohen-Tanugi\footnotemark[39],
\footnotetext[39]{Laboratoire Univers et Particules de Montpellier, Univ. Montpellier and CNRS, 34090 Montpellier, France} 
D.\ O.\ Jones\footnotemark[40],
\footnotetext[40]{University of California at Santa Cruz, Santa Cruz, CA 95064} 
Marc Kamionkowski\footnotemark[41],
\footnotetext[41]{Johns Hopkins University, Baltimore, MD 21218} 
Ryan E. Keeley\footnotemark[18],
Robert Kehoe\footnotemark[42],
\footnotetext[42]{Southern Methodist University, Dallas, TX 75275} 
Savvas M. Koushiappas\footnotemark[43],
\footnotetext[43]{Brown University, Providence, RI 02912} 
Ely D.~Kovetz\footnotemark[44],
\footnotetext[44]{Department of Physics, Ben-Gurion University, Be'er Sheva 84105, Israel} 
Kazuya Koyama\footnotemark[45],
\footnotetext[45]{Institute of Cosmology \& Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth PO1 3FX, UK} 
Benjamin L'Huillier\footnotemark[18],
Ofer Lahav\footnotemark[46],
\footnotetext[46]{University College London, WC1E 6BT London, United Kingdom} 
Chien-Hsiu Lee\footnotemark[47],
\footnotetext[47]{National Optical Astronomy Observatory, 950 N. Cherry Ave., Tucson, AZ 85719 USA} 
Michele Liguori\footnotemark[48],
\footnotetext[48]{Dipartimento di Fisica e Astronomia ``G. Galilei'',Universit\`a degli Studi di Padova, via Marzolo 8, I-35131, Padova, Italy} 
Axel de la Macorra\footnotemark[49],
\footnotetext[49]{IFUNAM - Instituto de F\'{i}sica, Universidad Nacional Aut\'onoma de M\'exico, 04510 CDMX, M\'exico} 
Joel Meyers\footnotemark[42],
Surhud More\footnotemark[50],
\footnotetext[50]{The Inter-University Centre for Astronomy and Astrophysics, Pune, 411007, India} 
Jeffrey A. Newman\footnotemark[21],
Gustavo Niz\footnotemark[51],
\footnotetext[51]{Divisi\'{o}n de Ciencias e Ingenier\'{i}as, Universidad de Guanajuato, Le\'{o}n 37150, M\'{e}xico} 
Antonella Palmese\footnotemark[28],
Francesco Piacentini\footnotemark[52]\textsuperscript{,}\footnotemark[53],
\footnotetext[52]{Dipartimento di Fisica, Universit\`{a} La Sapienza, P. le A. Moro 2, Roma, Italy} 
\footnotetext[53]{Istituto Nazionale di Fisica Nucleare, Sezione di Roma, 00185 Roma, Italy} 
Steven Rodney\footnotemark[54],
\footnotetext[54]{The University of South Carolina, Columbia, SC 29208} 
Benjamin Rose\footnotemark[55],
\footnotetext[55]{Space Telescope Science Institute, Baltimore, MD 21218} 
Masao Sako\footnotemark[56],
\footnotetext[56]{Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, Pennsylvania 19104, USA} 
Lado Samushia\footnotemark[57],
\footnotetext[57]{Kansas State University, Manhattan, KS 66506} 
Neelima Sehgal\footnotemark[58],
\footnotetext[58]{Stony Brook University, Stony Brook, NY 11794} 
Leonardo Senatore\footnotemark[34],
Sara Simon\footnotemark[13],
Stephanie Escoffier\footnotemark[59],
\footnotetext[59]{Aix Marseille Univ, CNRS/IN2P3, CPPM, Marseille, France} 
Scott Watson\footnotemark[60],
\footnotetext[60]{Syracuse University, Syracuse, NY 13244} 
Weishuang Xu\footnotemark[29],
Gong-Bo Zhao\footnotemark[61]\textsuperscript{,}\footnotemark[45],
\footnotetext[61]{National Astronomical Observatories, Chinese Academy of Sciences, PR China} 
Yi Zheng\footnotemark[62]
\footnotetext[62]{School of Physics, Korea Institute for Advanced Study, 85 Hoegiro, Dongdaemun-gu, Seoul 130-722, Korea}

>>>>

H.~Feldman\footnotemark[7],
\footnotetext[7]{Department of Physics \& Astronomy, University of Kansas, Lawrence, KS 66045-7550 USA}

@@

O.~Graur\footnotemark[8]\textsuperscript{,}\footnotemark[9]\textsuperscript{,}\footnotemark[10],
\footnotetext[8]{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
\footnotetext[9]{Department of Astrophysics, American Museum of Natural History, New York, NY 10024, USA}
\footnotetext[10]{NSF Astronomy and Astrophysics Postdoctoral Fellow}
R.~Graziani\footnotemark[11],
\footnotetext[11]{Universit\'e Clermont Auvergne, CNRS/IN2P3, Laboratoire de

@@

R.~Hlo\u{z}ek\footnotemark[3]\textsuperscript{,}\footnotemark[12],

@@

\footnotetext[12]{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, ON, M5S 3H4}
C.~Howlett\footnotemark[13],
\footnotetext[13]{International Centre for Radio Astronomy Research, The University of Western Australia, Crawley, WA 6009, Australia}
D.~Huterer\footnotemark[14],
\footnotetext[14]{Department of Physics, University of Michigan, 450 Church Street, Ann

@@

P.-F.~Leget\footnotemark[15],
\footnotetext[15]{Laboratoire de Physique Nucl\'eaire et de Hautes Energies, Sorbonne Universit\'e, CNRS-IN2P3, 4 Place Jussieu, 75005 Paris, France}    

@@

J.~Nordin\footnotemark[16],
\footnotetext[16]{Institut fur Physik, Humboldt-Universitat zu Berlin, Newtonstr. 15, 12489 Berlin, Germany}
P.~Nugent\footnotemark[17],
\footnotetext[17]{Computational Research Division, Lawrence Berkeley National Laboratory, 

@@

S.~Perlmutter\footnotemark[1]\textsuperscript{,}\footnotemark[18],
\footnotetext[18]{Department of Physics, University of California Berkeley, Berkeley, CA 94720}
N.~Regnault\footnotemark[15],

@@

M.~Rigault\footnotemark[11],

@@

A.~Shafieloo\footnotemark[19],
\footnotetext[19]{Korea Astronomy and Space Science Institute, Yuseong-gu, Daedeok-daero 776, Daejeon 34055, Korea}
A.~Slosar\footnotemark[20],
\footnotetext[20]{Brookhaven National Laboratory, Physics Department, Upton, NY

@@

R.~B.~Tully\footnotemark[21],
\footnotetext[21]{Institute for Astronomy, University of Hawaii, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
L.~Wang\footnotemark[22],
\footnotetext[22]{Texas A\&M University, College Station, TX 77843}
M.~White\footnotemark[1]\textsuperscript{,}\footnotemark[18],
M.~Wood-Vasey\footnotemark[23]
\footnotetext[23]{PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA} 

@@

\footnotemark[24],
\footnotetext[24]{Department of Physics, Lower Mountjoy, South Rd, Durham DH1 3LE, United Kingdom} 
Robert Armstrong\footnotemark[25],
\footnotetext[25]{Lawrence Livermore National Laboratory, Livermore, CA, 94550} 
Jacobo Asorey\footnotemark[19],
Carlo Baccigalupi\footnotemark[26]\textsuperscript{,}\footnotemark[27]\textsuperscript{,}\footnotemark[28],
\footnotetext[26]{SISSA - International School for Advanced Studies, Via Bonomea 265, 34136 Trieste, Italy} 
\footnotetext[27]{IFPU - Institute for Fundamental Physics of the Universe, Via Beirut 2, 34014 Trieste, Italy} 
\footnotetext[28]{INFN - National Institute for Nuclear Physics, Via Valerio 2, I-34127 Trieste, Italy} 
Maciej Bilicki\footnotemark[29],
\footnotetext[29]{Center for Theoretical Physics, Polish Academy of Sciences, al. Lotnik\'{o}w 32/46, 02-668, Warsaw, Poland} 
Julian Borrill\footnotemark[17], 
Elizabeth Buckley-Geer\footnotemark[30],
\footnotetext[30]{Fermi National Accelerator Laboratory, Batavia, IL 60510} 

@@

Cora Dvorkin\footnotemark[31],
\footnotetext[31]{Department of Physics, Harvard University, Cambridge, MA 02138, USA} 
Simon Foreman\footnotemark[32],
\footnotetext[32]{Canadian Institute for Theoretical Astrophysics, University of Toronto, Toronto, ON M5S 3H8, Canada} 
Llu\'is Galbany\footnotemark[23],
Juan Garc\'ia-Bellido\footnotemark[33]\textsuperscript{,}\footnotemark[34],
\footnotetext[33]{Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain} 
\footnotetext[34]{Universidad Aut\'{o}noma de Madrid, 28049, Madrid, Spain} 
Martina Gerbino\footnotemark[35],
\footnotetext[35]{HEP Division, Argonne National Laboratory, Lemont, IL 60439, USA} 
Mandeep S.S. Gill\footnotemark[36]\textsuperscript{,}\footnotemark[37]\textsuperscript{,}\footnotemark[38],
\footnotetext[36]{Kavli Institute for Particle Astrophysics and Cosmology, Stanford 94305} 
\footnotetext[37]{Stanford University, Stanford, CA 94305} 
\footnotetext[38]{SLAC National Accelerator Laboratory, Menlo Park, CA 94025} 
Larry Gladney\footnotemark[39],
\footnotetext[39]{Department of Physics, Yale University, New Haven, CT 06520} 
Saurabh W.~Jha\footnotemark[40],
\footnotetext[40]{Department of Physics and Astronomy, Rutgers, the State University of New Jersey, 136 Frelinghuysen Road, Piscataway, NJ 08854, USA} 
Johann Cohen-Tanugi\footnotemark[41],
\footnotetext[41]{Laboratoire Univers et Particules de Montpellier, Univ. Montpellier and CNRS, 34090 Montpellier, France} 
D.\ O.\ Jones\footnotemark[42],
\footnotetext[42]{University of California at Santa Cruz, Santa Cruz, CA 95064} 
Marc Kamionkowski\footnotemark[43],
\footnotetext[43]{Johns Hopkins University, Baltimore, MD 21218} 
Ryan E. Keeley\footnotemark[19],
Robert Kehoe\footnotemark[44],
\footnotetext[44]{Southern Methodist University, Dallas, TX 75275} 
Savvas M. Koushiappas\footnotemark[45],
\footnotetext[45]{Brown University, Providence, RI 02912} 
Ely D.~Kovetz\footnotemark[46],
\footnotetext[46]{Department of Physics, Ben-Gurion University, Be'er Sheva 84105, Israel} 
Kazuya Koyama\footnotemark[47],
\footnotetext[47]{Institute of Cosmology \& Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth PO1 3FX, UK} 
Benjamin L'Huillier\footnotemark[19],
Ofer Lahav\footnotemark[48],
\footnotetext[48]{University College London, WC1E 6BT London, United Kingdom} 
Chien-Hsiu Lee\footnotemark[49],
\footnotetext[49]{National Optical Astronomy Observatory, 950 N. Cherry Ave., Tucson, AZ 85719 USA} 
Michele Liguori\footnotemark[50],
\footnotetext[50]{Dipartimento di Fisica e Astronomia ``G. Galilei'',Universit\`a degli Studi di Padova, via Marzolo 8, I-35131, Padova, Italy} 
Axel de la Macorra\footnotemark[51],
\footnotetext[51]{IFUNAM - Instituto de F\'{i}sica, Universidad Nacional Aut\'onoma de M\'exico, 04510 CDMX, M\'exico} 
Joel Meyers\footnotemark[44],
Surhud More\footnotemark[52],
\footnotetext[52]{The Inter-University Centre for Astronomy and Astrophysics, Pune, 411007, India} 
Jeffrey A. Newman\footnotemark[23],
Gustavo Niz\footnotemark[53],
\footnotetext[53]{Divisi\'{o}n de Ciencias e Ingenier\'{i}as, Universidad de Guanajuato, Le\'{o}n 37150, M\'{e}xico} 
Antonella Palmese\footnotemark[30],
Francesco Piacentini\footnotemark[54]\textsuperscript{,}\footnotemark[55],
\footnotetext[54]{Dipartimento di Fisica, Universit\`{a} La Sapienza, P. le A. Moro 2, Roma, Italy} 
\footnotetext[55]{Istituto Nazionale di Fisica Nucleare, Sezione di Roma, 00185 Roma, Italy} 
Steven Rodney\footnotemark[56],
\footnotetext[56]{The University of South Carolina, Columbia, SC 29208} 
Benjamin Rose\footnotemark[57],
\footnotetext[57]{Space Telescope Science Institute, Baltimore, MD 21218} 
Masao Sako\footnotemark[58],
\footnotetext[58]{Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, Pennsylvania 19104, USA} 
Lado Samushia\footnotemark[59],
\footnotetext[59]{Kansas State University, Manhattan, KS 66506} 
Neelima Sehgal\footnotemark[60],
\footnotetext[60]{Stony Brook University, Stony Brook, NY 11794} 
Sara Simon\footnotemark[14],
Stephanie Escoffier\footnotemark[61],
\footnotetext[61]{Aix Marseille Univ, CNRS/IN2P3, CPPM, Marseille, France} 
Scott Watson\footnotemark[62],
\footnotetext[62]{Syracuse University, Syracuse, NY 13244} 
Weishuang Xu\footnotemark[31],
Gong-Bo Zhao\footnotemark[63]\textsuperscript{,}\footnotemark[47],
\footnotetext[63]{National Astronomical Observatories, Chinese Academy of Sciences, PR China} 
Yi Zheng\footnotemark[64]
\footnotetext[64]{School of Physics, Korea Institute for Advanced Study, 85 Hoegiro, Dongdaemun-gu, Seoul 130-722, Korea}
